Empirical Analysis of Performance Bottlenecks in Graph Neural Network Training with GPUs

### 2020-12-16 NEUROC/Response-MajRev/response_letter.tex

% !TEX program=pdflatex
% LaTeX rebuttal letter example. 
% 
% Copyright 2019 Friedemann Zenke, fzenke.net
%
% Based on examples by Dirk Eddelbuettel, Fran and others from 
% https://tex.stackexchange.com/questions/2317/latex-style-or-macro-for-detailed-response-to-referee-report
% 
% Licensed under cc by-sa 3.0 with attribution required.

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{lipsum} % to generate some filler text
\usepackage{fullpage}
\usepackage{times}
\usepackage{amsmath, amsthm}

@@

\section*{Response to the reviewers}
% General intro text goes here
We thank the reviewers for their critical assessment of our work. 
In the following we address their concerns point by point.

% Let's start point-by-point with Reviewer 1
\reviewersection

% Point one description 
\begin{point}
	There are lots of symbols in this paper. Some symbols are reused and confusing, such as s denotes sub-layers or edge features.
\end{point}

% Our reply
\begin{reply}
    We apologize for the confusing use of symbols.
    %
    To clarify the symbol usage, we have checked the full text of the manuscript and unified the usage of symbols.
    %
    We have avoided the problem of repeated use of symbols, so that each symbol only represents one meaning after the revision.
    %
    We summarize the frequently-used symbols in Table 1 in the revised manuscript.
    %
    We quote the table below:
    %%%%% TODO, Paste Table 1 %%%%.

    In the revised manuscript, $\boldsymbol{e}_{i,j}$ represents the input feature vector of the edge $e_{i,j}$.
    %
    It is the same for all GNN layers.
    %
    $\boldsymbol{s}$ represents aggregated vectors outputted by the aggregation function $\Sigma$ in graph neurons.
    %
    $\boldsymbol{s}^l_i$ represents the aggregated vector of the graph neuron corresponding to the vertex $v_i$ in the GNN layer $l$.
    %
    If the GNN layer $l$ has sub-layers, $\boldsymbol{s}^{l,k}_i$ represents the aggregated vector corresponding to $v_i$ in the $k$-th sub-layer.

    To clarify the concept of sub-layers in a GNN layer, we have added the following description in Section 2.2 ``Graph Neuron and Message-passing Model'' in the revised manuscript:
    %%%%% TODO %%%%%%%%

\end{reply}

### 2020-12-16 NEUROC/sec2-review-of-graph-neural-network.tex
update
增加了Motivation各个数据集的代码
更新R1P1

\section{Review of Graph Neural Networks}
\label{sec:review_of_gnns}

In this section, we formally define the graph neural networks and briefly survey typical graph neural networks.
We denote a simple graph $\mathcal{G}$ as $\mathcal{G}=(\mathcal{V}, \mathcal{E})$, where $\mathcal{V}$ and $\mathcal{E}$ are the vertex set and the edge set of $\mathcal{G}$, respectively.
Let $n=|\mathcal{V}|$ and $m=|\mathcal{E}|$ as the number of vertices/edges.
We use $v_i$ $(0 \leq i < n)$ to denote a vertex and $e_{i,j}=(v_i, v_j)$ to denote the edge pointing from $v_i$ to $v_j$.
The adjacency set of $v_i$ is $\mathcal{N}(v_i)=\{v|(v_i, v) \in \mathcal{E}\}$.
We denote a \emph{vector} with a bold lower case letter like $\boldsymbol{x}$ and a \emph{matri}x with a bold upper case letter like $\boldsymbol{X}$.

@@

>>>>

% !TEX root=ms.tex
\section{Review of Graph Neural Networks}
\label{sec:review_of_gnns}

In this section, we formally define the graph neural networks and briefly survey typical graph neural networks.
We denote a simple \emph{undirected} graph $\mathcal{G}$ as $\mathcal{G}=(\mathcal{V}, \mathcal{E})$, where $\mathcal{V}$ and $\mathcal{E}$ are the vertex set and the edge set of $\mathcal{G}$, respectively.
%Let $n=|\mathcal{V}|$ and $m=|\mathcal{E}|$ as the number of vertices/edges.
We use $v_i$ $(0 \leq i < |\mathcal{V}|)$ to denote a vertex and $e_{i,j}=(v_i, v_j)$ to denote the edge pointing from $v_i$ to $v_j$.
The adjacency set of $v_i$ is $\mathcal{N}(v_i)=\{v|(v_i, v) \in \mathcal{E}\}$.
We denote a \emph{vector} with a bold lower case letter like $\boldsymbol{x}$ and a \emph{matri}x with a bold upper case letter like $\boldsymbol{X}$.
Table~\ref{tab:notations} summarizes the common symbols used throughout this work.

\begin{table}[h]
    \caption{Notations}
    \label{tab:notations}
    \centering
    \small
    \begin{tabular}{p{3em}lp{35em}}
        \toprule
       Category & Symbol & Meaning \\
        \midrule
        \multirow[c]{4}{3em}{Graph Structure}& $\mathcal{G}=(\mathcal{V}, \mathcal{E})$ & The simple undirected input graph with the vertex set $\mathcal{V}$ and the edge set $\mathcal{E}$. \\
        & $v_i$ & The $i$-th vertex of the input graph. \\
        & $e_{i,j}$ & The edge pointing from $v_i$ to $v_j$ of the input graph. \\
        & $\mathcal{N}(v_i)$ & The adjacency set of $v_i$ in the input graph. \\ \midrule
        \multirow[c]{6}{3em}{GNN Definition}& $L$ & The number of GNN layers. \\
        & $\phi^l$ & The messaging function of the GNN layer $l$. \\
        & $\Sigma^l$ & The aggregation function of the GNN layer $l$. \\
        & $\gamma^l$ & The vertex updating function of the GNN layer $l$. \\ 
        & $\phi^{l,k}$/$\Sigma^{l,k}$/$\gamma^{l,k}$ & The messaging/aggregation/updating function of the $k$-th sub-layer of the GNN layer  $l$.\\
        & $\textcolor{blue}{\boldsymbol{W}^l, \boldsymbol{W}^{(k)}/\boldsymbol{b}, \boldsymbol{a}}$ & The matrices/vectors represented by the blue characters are the weight matrices/vectors that need to be learned in the GNN. \\  \midrule
        \multirow[c]{8}{3em}{Vectors}& $\boldsymbol{v}_i$ & The input feature vector of the vertex $v_i$. \\
        & $\boldsymbol{e}_{i,j}$ & The input feature vector of the edge $e_{i,j}$.  \\
        & $\boldsymbol{h}_i^{l}$ &  The {input} hidden vector of the graph neuron corresponding to $v_i$ in the GNN layer $l$. \\
        & $\boldsymbol{h}_i^{l+1}$ &  The {output} hidden vector of the graph neuron corresponding to $v_i$ in the GNN layer $l$.\\
        & $\boldsymbol{m}_{i,j}^l$ & The message vector of the edge $e_{i,j}$ outputted by $\phi^l$ of the GNN layer $l$. \\
        & $\boldsymbol{s}_{i}^l$ & The aggregated vector of the vertex $v_i$ outputted by $\Sigma^l$ of the GNN layer $l$. \\
        & $\boldsymbol{m}_{i,j}^{l,k}$/$\boldsymbol{s}_{i}^{l,k}$ & The message/aggregated vector of the vertex $v_i$ outputted by $\phi^{l,k}$/$\Sigma^{l,k}$ of the $k$-th sub-layer of the GNN layer $l$. \\
        & $d_{in}$, $d_{out}$ &  The dimensions of the input/output hidden vectors of a graph neuron. \\
        \bottomrule

    \end{tabular}
\end{table}

@@

    \hspace{-5em}
